%-------------------------
% Resume in Latex
% Author : Harnish Gemlawala
% Based off of: https://github.com/HarnishGemlawala
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Harnish Gemlawala} \\ \vspace{3pt}
    \small 647-614-7330 $|$ \href{mailto:harnishgemlawala02@gmail.com}{\underline{harnishgemlawala02@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/harnish-gemlawala-25a866135/}{\underline{linkedin.com/in/harnish-gemlawala}} $|$
    \href{https://github.com/HarnishGemlawala}{\underline{github.com/HarnishGemlawala}}
\end{center}

%-----------Technical SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java-J2EE, Python, SQL (Oracle), JavaScript, HTML/CSS, Ajax} \\
     \textbf{Frameworks}{: Struts2, React, Node.js, JUnit, RESTful services, Spring, TortoiseSVN } \\
     \textbf{Developer Tools}{: Git, VS Code, PyCharm, IntelliJ, Eclipse} \\
     \textbf{Libraries}{: Hibernate, Bootstrap, Google GSON, SoapUI WSDL , NumPy }\\
     \textbf{Other Softwares}{: MATLAB Script and Simulink, AutoCAD 3D Design, AutoCAD Electrical, MS Office tools: Excel, Outlook, Teams, Word, PowerPoint }
    }}
 \end{itemize}


%-------------------------------------------

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Windsor}{Windsor, ON}
      {Master of Engineering in Electrical and Computer Engineering}{May 2022 -- August 2023}
    \resumeSubheading
      {Gujarat Technological University}{Surat, India}
      {Bachelor of Engineering in Electrical Engineering}{July 2016 -- August 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Production Operator}{September 2023 -- Present}
      {The Job Shopee (Vista Print) }{Windsor, ON}
      \resumeItemListStart
        \resumeItem{Operated and maintained printing machinery at Vistaprint, ensuring seamless production. Conducted quality checks, reducing defects. }
        \resumeItem{  Collaborated with teams to meet production targets and assisted new members.}
        \resumeItem{Executed routine equipment maintenance, minimizing downtime.}
        \resumeItem{Adhered to safety protocols, contributing to a zero-accident record.}
        \resumeItem{Given appreciation by Production Coordinator for meeting targets and maintaining high standards.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Student Advisor}{December 2022 -- August 2023}
      {University of Windsor (International Student Centre)}{Windsor, ON}
      \resumeItemListStart
        \resumeItem{Provided guidance and support to international students for academic success. Assisted students with visa regulations, immigration documents, and cultural adaptation}
        \resumeItem{Organized orientation programs and workshops to enhance students' integration experience.}
        \resumeItem{Fostered a welcoming and inclusive environment, addressing students' concerns and needs.}
    \resumeItemListEnd

    \resumeSubheading
      {Web Application Developer}{April 2021 -- April 2022}
      {Wipro Limited}{Pune, India}
      \resumeItemListStart
        \resumeItem{Mastered Java J2EE, HTML, CSS, JavaScript, and frameworks. Enhanced skills through online courses and projects.}
        \resumeItem{Applied Lean and Agile methods, driving process efficiency.}
        \resumeItem{Honed client communication skills for effective solutions. Developed REST API, Soap WSDL for seamless telecom service ticketing between companies.}
        \resumeItem{Automated server check system, dynamic alerts for swift issue resolution. Designed user portal for top telecom provider.}
        
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%-----------Internship-----------
\section{Internship}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Research Assitant}{August 2019 -- September 2020}
      {Rollscoax}{Surat, India}
      \resumeItemListStart
        \resumeItem{Developed a REST API using FastAPI and PostgreSQL to store data from learning management systems}
        \resumeItem{Developed a full-stack web application using Flask, React, PostgreSQL and Docker to analyze GitHub data}
        \resumeItem{Explored ways to visualize GitHub collaboration in a classroom setting}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AES Encryption design and Vigenere Cipher} $|$ \emph{Python,NumPy, Java}}{January 2023 -- April 2023}
          \resumeItemListStart
            \resumeItem{Implemented Advanced Encryption Standard (AES) algorithm using Python and the later with Java, ensuring secure data encryption.}
            \resumeItem{Developed robust encryption functionality, adhering to industry best practices and data security standards.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Smart parking system} $|$ \emph{MATLAB Script}}{November 2022 -- December 2022}
          \resumeItemListStart
            \resumeItem{Designed a pin authentication-based parking system with User Identification and parking spot allotment.}
            \resumeItem{Implemented this design using MATLAB scripting and Arduino micro controller for Pin authentication, spot allotment and User display.}
          \resumeItemListEnd
       \resumeProjectHeading
          {\textbf{Telecomm API Development} $|$ \emph{ Java, Struts2, Spring, Javascript, REST api, WSDL}}{June 2021 -- April 2022}
          \resumeItemListStart
            \resumeItem{Integrated JSON and XML communication channels using Gson Rest API and SoapUI for API connections.}
            \resumeItem{Optimized SQL databases with efficient Queries, Procedures, Triggers for Disaster Recovery.}
            \resumeItem{Transformed MPA module into a dynamic Single Page App and upgraded to Angular 10, AJAX, and Strut2.}
            \resumeItem{Recognized for client management, exceptional service, and upgrading ticketing systems, fostering commendation}
          \resumeItemListEnd
     \resumeProjectHeading
          {\textbf{Vertical Crawling Inspection ROBOT} $|$ \emph{AutoCAD 3D Design, MATLAB Script}}{August 2019 -- August 2020}
          \resumeItemListStart
            \resumeItem{Designed 3D Chassis model of Vertical Crawling ROBOT for Metallic Surface Inspection using AutoCAD.}
            \resumeItem{Developed a wireless crawler ROBOT with Camera and Probe mounting with magnet gripping wheels.}
            \resumeItem{Successfully Tested the ROBOT for thickness measurement and Visual inspection in  \emph{Arcellar Mittal and Nippon Steel} Industry at higher altitude.}
          \resumeItemListEnd    
    \resumeSubHeadingListEnd



%

\end{document}
